### 2025-04-27 conteudo/introduction/intro.tex
add comments on todos for the dissertation text
some changes to better reflect the change of the focus of the research

@@

@@

@@

@@

This research aims to identify patterns of software engineering techniques, such as refactoring methods commonly used to address code duplications. These patterns will serve as a guide for future contributors in mitigating code duplication issues within this context. To investigate our approach, we are developing a tool to identify duplicate code in the Linux kernel, explicitly targeting parts of the AMD Display driver code. We are then refactoring portions of this code and submitting patches to maintainers, providing evidence of the tool's accuracy in detecting duplicate functions. Our research design follows a multi-method approach, structured into two phases, each employing different research methods.

@@

Upon completing the first phase, we anticipate having a validated tool for
identifying code duplications within the Linux kernel context. We will then
proceed to the second phase, which focuses on strategies for mitigating these
duplications. In \textbf{Phase II}, our objective is to identify practical
approaches to address the code duplications detected in the Linux kernel. To
achieve this, we have designed an ethnographic approach that enables us to
interact with the Linux development community and gather artifacts that either
support or challenge our proposed mitigation strategies. Figure
\ref{fig:reDesign} summarizes the research steps proposed in this study.

>>>>

\todo[inline]{Require updated information about the linux kernel. Required from qualification exam.}

@@

\todo[inline]{Maybe talk about the tests on IIO software, as the test is not tested only on AMD Display driver anymore. Maybe mention the tool explicitly.}

@@

\todo[inline]{THIS SECTION NEEDS TO BE REMADE FROM ZERO.}

@@

\todo[inline]{Focus more on the tool here.}

@@

This research aims to identify patterns of software engineering techniques, 
such as refactoring methods commonly used to address code duplications. 
These patterns will serve as a guide for future contributors in mitigating 
code duplication issues within this context. To investigate our approach, 
we are developing a tool to identify duplicate code in the Linux kernel, 
explicitly targeting parts of the AMD Display driver code and the IIO driver. We are then refactoring 
portions of this code and submitting patches to maintainers, providing evidence 
of the tool's accuracy in detecting duplicate functions. Our research design follows 
a multi-method approach, structured into two phases, each employing different research methods.

@@

Upon completing the first phase, we anticipate having a validated tool for
identifying code duplications within the Linux kernel context. We will then
proceed to the second phase, which focuses on mitigating these
duplications. In \textbf{Phase II}, our objective is to verify if we can 
practically mitigate the duplication finds by the developed tool. 
To achieve this, we have designed an ethnographic approach that enables us to
interact with the Linux development community and gather artifacts that either
support or challenge our proposed mitigation strategies. Figure
\ref{fig:reDesign} summarizes the research steps proposed in this study.

### 2025-04-27 conteudo/methods/methods.tex
some changes to better reflect the change of the focus of the research

We employ a multi-method research approach, using different methodologies to achieve our goals. Our first choice is to conduct an ethnographic study using a participant-observation methodology. In this study, we aim to mitigate a subset of duplicated functions by refactoring them systematically while interacting with the Linux community to gather feedback on our mitigation efforts. To address our main objective of mitigating code duplication in the Linux kernel, we first needed the ability to identify these duplications accurately. Thus, we developed a tool and assessed its capability to detect code duplications in the Linux kernel.

We applied two independent methods and perform triangulation on the results. 
The first method evaluates the proposed tool using an approach from the literature, 
comparing it against the BigCloneBench dataset \citep{bigclonebench}. 
The second method is an empirical analysis of a subset of functions within the 
AMD Display driver that our tool identified as duplicates. After completing these two 
methods, we triangulated the findings to analyze the results comprehensively. 
We chose triangulation because relying solely on the literature-based method has 
limitations and may not be entirely reliable \citep{bigfail, litreview}.

>>>>

We employ a multi-method research approach, using different methodologies to achieve our goals
to approach code duplication in some of the Linux subsystems. 
To validate if the Arkanjo tool is capable of finding code duplications, 
applied two independent methods and perform triangulation on the results.

The first method evaluates the proposed tool using an approach from the literature, 
comparing it against the BigCloneBench dataset \citep{bigclonebench}. 
The second method is an empirical analysis of a subset of functions within the 
AMD Display driver that our tool identified as duplicates. After completing these two 
methods, we triangulated the findings to analyze the results comprehensively. 
We chose triangulation because relying solely on the literature-based method has 
limitations and may not be entirely reliable \citep{bigfail, litreview}. As a reminder, 
all research approches were done using the text similarity method as the 
code dupication method of the tool.

Given the validation of the tool's capabilities, we proceed to undertand the viability 
to mitigate the code duplication finds by the tool. 
To underdand the viability, our first choice is to conduct an ethnographic study using 
a participant-observation methodology. 
In this study, we aim to mitigate a subset of duplicated functions by refactoring them 
while interacting with the Linux community to gather feedback on our mitigation efforts.

The ethnographic study happened in two phases. 
In the first phase, the author of this research explored the process of mitigating
a code duplication found in the AMD Display Driver and sent it as a PATCH to iteract with the
Linux community and get their feedback. On a second phase, we proposed to students on the 
course Free Software Development at University São Paulo to mitigate the code duplications found 
by the tool in the IIO and AMD Display Driver and pass the process of send the mitigations as PATCH.
(DOUBLE CHECK IF THE STUDENTS HAVE SENT THE PATCHES).

I
